---
title: "Unit 1 - 3 Review Starter"
author: "TALC group 1"   
date: "10/4/2021"
output: html_document 
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sand_minerals <- read_csv("data/sand-minerals.csv")
location_descriptions <- read_csv("data/location-descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility-hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals} 

glimpse(sand_minerals)
names(sand_minerals)

```

There are `r nrow(sand_minerals)` rows and `r ncol(sand_minerals)` columns

### Exercise 2

```{r inspect-other-dataframes}

glimpse(location_descriptions) 
glimpse(density) 
glimpse(solubility_hardness) 
names(location_descriptions) 
names(density) 
names(solubility_hardness) 

```

In location_descriptions there are `r nrow(location_descriptions)` rows and `r ncol(location_descriptions)`, in density there are `r nrow(density)` rows and `r ncol(density)`, and in solubility_hardness there are `r nrow(solubility_hardness)` rows and `r ncol(solubility_hardness)`.

For location_descriptions, the rows are the location number and the location description. For density, the rows are the mineral names and their density. For solubility_hardness, the rows are the mineral names, the solubility, and the hardness.

### Exercise 3

```{r join-mineral-properties}
sand_mineral_density <- density %>%
  left_join(sand_minerals)

glimpse(sand_mineral_density)

```

This new table appears to have 23 outputs (rows), which is the same as the number of outputs for sand_minerals.

```{r sand-mineral-properties}

sand_mineral_properties <- solubility_hardness %>%
  left_join(sand_mineral_density)

glimpse(sand_mineral_properties)
```


### Exercise 4

```{r - mineral-locations}
sand_mineral_properties %>%
  count(location)

```

```{r - sandmineralsselectedlocations}
sand_mineral_properties %>%
slice(14:24) 
```

```{r - sandmineraldensity}
sand_mineral_properties %>%
  arrange(desc(density)) %>%
slice(13:23)

```

```{r - sandmineraldensityselected}
sand_mineral_properties %>%
  select(1, 5) %>%
slice(18:23)
```

```{r - sandmineralsimportantvalues}
sand_mineral_properties %>%
  filter(!is.na(hardness)) %>%
arrange(desc(density)) %>%
slice(1:5)

```
### Exercise 5

Test with test account

### Exercise 6

Deleted exercise 1 text as test of fork.
